\chapter{State of the Art}
\graphicspath{{state-of-the-art/figures/}}

In recent years, the remarkable advancements in Natural Language Processing (NLP) have been primarily driven by the development of LLMs. These LLMs, such as GPT (Generative Pretrained Transformer)\cite{openai:gpt} and BERT (Bidirectional Encoder Representations from Transformers)\cite{devlin2019bert}, have demonstrated remarkable capabilities in understanding and generating human-like text. However, despite their impressive performance, LLMs still face challenges in effectively retrieving and incorporating relevant context for generating accurate and coherent responses.

Enter RAG systems, a novel approach that seeks to overcome the limitations of traditional LLMs by integrating retrieval mechanisms with generation models. RAG systems combine the strengths of both retrieval and generation techniques to enhance the quality and relevance of generated text.

This chapter provides a comprehensive exploration of RAG systems, delving into their architecture, components, training processes, applications, advantages, and challenges. We begin by establishing a foundational understanding of LLMs and their evolution, laying the groundwork for understanding the need for RAG systems. We then proceed to dissect the intricacies of RAG systems, discussing the role of retrieval in providing context and the role of generation in producing fluent responses.

Through detailed examination and analysis, we uncover the inner workings of RAG systems, exploring how retrieval and generation components interact within the architecture. Real-world applications and use cases of RAG systems across various domains are elucidated, demonstrating their potential to revolutionize tasks such as question answering, dialogue generation, and content creation. Furthermore, we evaluate the advantages and limitations of RAG systems compared to traditional LLMs and other approaches in NLP.

In summary, this chapter serves as a comprehensive guide to RAG systems, offering readers a deep dive into one of the most promising advancements in NLP. As we navigate through the complexities and potentials of RAG systems, we pave the way for understanding their role in shaping the future of human-computer interaction and language understanding.

\input{state-of-the-art/sections/ml}

\input{state-of-the-art/sections/dl}

\clearpage

\input{state-of-the-art/sections/nlp}

\clearpage

\input{state-of-the-art/sections/neural-networks}

\clearpage

\input{state-of-the-art/sections/transformers}

\clearpage

\input{state-of-the-art/sections/llms}

\clearpage

\input{state-of-the-art/sections/rag}